\documentclass{article}
\usepackage[UTF8]{ctex}
\usepackage{multicol}
\usepackage{amsmath}
\usepackage{chngpage}
\usepackage{indentfirst}
\usepackage{graphicx}
\begin{document}
\setlength{\parindent}{2em}
\title{Lab4-Report}
\author{517030910412 陆晗}
\date{2020.5.18}
\maketitle
	
\paragraph{Design decision}
\subparagraph{Eviction policy} 
I use the histogram for selectivity estimation. And I have some boundary cases. Just like the size of last bucket. If the number of buckets is larger than the range. My solution is that the buckets are equal size unless the last one. And the last one may be larger. If the number is larger, I will make it equal to the range. For join ordering, I just follow the instruction of the document. 


\paragraph{API}

No change for API.

\paragraph{Incomplete elements}

I think none. If there exits, thanks very much to inform me and I will fill the hole as soon as quickly. 

\paragraph{Others}
I spent \textbf{two days} in finishing the code. 
Fisrt I passed all the units test, I was so excited. But I found I time-out in the query test. I was so confused and I check my implement of the functions to make sure I didn't write the algorithm wrong to make them slow. I gradually tracked down the problem using debug step by step.It is the  numpage() maybe need IO operation and division calculation. This will cost much time. And I did some structure change in the heapfile iterator implement to reduce the call of the function. Good habits are really important.

\end{document}